Approximation as Differentiation

### 2025-05-24 main/framework.tex
Slow prog..

This pattern of objects and morphisms is captured by the construction used in CHAD~\cite{vákár22,nunes2023} to
describe automatic differentiation, namely the \emph{Grothendieck construction} for a particular indexed
category $T: \Set^\op \to \Cat$. For CHAD $T(X)$ is the functor category $\Func{X}{\FinVect}$, regarded as the
category of $X$-indexed families of finite vector spaces, with ; here $T(X) = \Func{X}{\LatGal}$, the category of
$X$-indexed families of bounded lattices, with $X$-indexed families of Galois connections between them as
morphisms. The Grothendieck construction $\Grothendieck{}T$~(\defref{Grothendieck} below) for an indexed
category $T$, sometimes called the \emph{total category} for $T$, is the category of all $\Set$-indexed
families of objects of $T$, together with morphisms that account for both structure within each family and how
families transform under reindexing.

>>>>

This pattern of objects and morphisms is captured by the construction used in CHAD~\cite{vákár22,nunes2023} to
describe automatic differentiation, namely the \emph{Grothendieck construction} for a particular indexed
category $T: \Set^\op \to \Cat$. For CHAD $T(X)$ will be the functor category $\Func{X}{\FinVect}$, regarded
as the category of $X$-indexed families of finite vector spaces, with indexed linear maps; here $T(X) =
\Func{X}{\LatGal}$, the category of $X$-indexed families of bounded lattices, with indexed Galois connections
as morphisms. The Grothendieck construction $\Grothendieck{}T$~(\defref{Grothendieck} below) for an indexed
category $T$, sometimes called the \emph{total category} for $T$, is the category of all $\Set$-indexed
families of objects of $T$, together with morphisms that account for both structure within each family and how
families transform under reindexing.
